Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2020-06-25 write-up/fda-recurrent.tex
putting sim to run on servers

@@

@@

@@

>>>>

\begin{itemize}
\item Sample every 0.5 hours; then subsample at each subrate. Estimates are given by $\hat \beta_{i,0.5} (t)$ and $\hat \beta_{i,1} (t)$.
\item Bias is average over the estimates $\bar \hat \beta_{0.5} (t) = 100^{-1} \sum_{i=1}^100 \hat \beta_{i, 0.5} (t)$ compared to truth.
\item Take squared difference integrated to get variance.
\item To get the subsampling variance take $1/1000 \sum_{i=1}^1000 (\hat \beta_{i,0.5} (t) - \hat \beta_{i,1} (t))^2$.
\item Normalize everything by squared function!
\end{itemize}

@@

\begin{equation}
\label{eq:multihazardlinear}
h_i \left( t \given  H_{i,t}^{NX} ; \theta \right) =
h_0 (t; \gamma) \exp \left( g_t \left( H_{i,t}^{N} \right)^{\prime} \alpha
  + \int_{t-\Delta}^t x_{1i} (s) \beta_1(s) ds + \int_{t-\Delta}^t x_{2i} (s) \beta_2(s) ds  \right)
\end{equation}

@@

\begin{equation}
\label{eq:multilevel}
h_i \left( t \given  H_{i,t}^{NX} ; \theta, b_i \right) \approx
\exp \left( Z_{t}^\top \gamma + g_t \left( H_{i,t}^{N} \right)^{\prime} \alpha
  + \left[ M_{i,t}^\top + C_{i,t}^\top J_{\hat \psi, \phi}\right] (\beta + b_i) \right)
= \exp \left( W_{i,t}^\top \theta  + Z_{i,t}^\top b_i \right),
\end{equation}

@@

\textcolor{red}{Assume fixed $\lambda$.}
